### 2018-04-29 paper/conclusion.tex
Writes up security analysis
I must write a system and adversary model, then adapt the security
analysis to them.

\section{Conclusion and Future Work}

@@

% \commentAL{To rewrite as real paragraphs} Future work and prospects:
% \begin{itemize}
% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
% 	\item Changing devices' asymmetric keys regularly would increase security.
% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver. To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.

% \end{itemize}

We see two alternative paths for improving the header.
First, we might be able to adapt the Sphinx~\cite{Sphinx} cryptographic packet 
format to the routing of \(\SPOR\).
Then we could achieve the properties of Sphinx and enjoy provable security.

The second approach would be to use the technique by \textcite{PPACinPubFS}.
They adapt \(\ANOBE\) in such a way that its ciphertexts decrypt to different 
things for different recipients.
This way we could have one ciphertext encrypted for all the alternative nodes 
--- across layers.
Then the ciphertext would decrypt to different plaintexts for nodes on different 
layers in the route.
This would hide the path length (constant-size ciphertexts by padding) and the 
position of individual nodes.
This approach would probably be the easiest, but would probably not provide all 
the properties from Sphinx (\eg resistance to active tagging attacks and bitwise 
unlinkability).

>>>>

\section{Conclusion and Future Work}%
\label{conclusion}

@@

### 2018-04-29 paper/related.tex

P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster), availability and replication (Gnutella), scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}, and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview). In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person. Here, we focus on sharing files in a more deliberate yet ad-hoc manner, i.e., between users that out-of-band agree to share a file but do not keep it available for anyone else in the future. TOR~\cite{Tor}, although not designed for file sharing specifically, comes closest in that respect, but does not address the following aspect.

>>>>

Mixnets~\cite{Chaum:198} are perhaps the first solution to turn to for sending content from A to B anonymously. In our context, however, they are less suitable due to their reliance on mix servers, the limited protection against statistical inference possible for even a perfect mixnet given the multiple varying sources and destinations of our use case, and the delay they would add due to batching. We thus decided for an approach based on onion routing.

P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster, then decentralized Gnutella), availability and replication~\cite{replica}, scalability (Bittorrent~\cite{bittorrent}), anonymity (Freenet~\cite{freenet}, TOR~\cite{Tor}), and distributed hash tables (DHT) such as CAN, Chord, Pastry, and Tapestry (see \cite{dhtchurn} for an overview). In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person. Here, we focus on sharing files in a more deliberate yet ad-hoc manner, i.e., between users that out-of-band agree to share a file but do not keep it available for anyone else in the future. TOR~\cite{Tor}, although not designed for file sharing specifically, comes closest in that respect, but does not address the following aspect.

### 2018-04-29 paper/security-analysis.tex

What makes sense is to choose at least an authenticated encryption 
scheme~\cite{AuthEncryption}.
(We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, 
\eg the one by \textcite{OTPKX} which is both deniable and authenticated and 
provides \ac{DEN-SS}.)
This would give confidentiality (or deniability) and integrity for the message, 
but if the first and the last node belong to Carol and David, they can infer 
that Alice sent a message to Bob.
Note that as our in-package header is designed, each node on the route can infer 
its position on the route \emph{relative to the destination}.
(We discuss how to remedy this in \cref{conclusion}.)
None of the nodes can know if they are the first node or not, unless they 
collude with the previous node.
The last node, however, can know for sure that the next hop is the destination, 
but not who it belongs to.

@@

% \commentAL{To rewrite as real paragraphs} Future work and prospects:
% \begin{itemize}
% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
% 	\item Changing devices' asymmetric keys regularly would increase security.
% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver. To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.

>>>>

What makes sense is to choose at least an authenticated encryption 
scheme~\cite{AuthEncryption}.
(We could also choose a deniable encryption scheme~\cite{DeniableEncryption}, 
\eg the one by \textcite{OTPKX} which is both deniable and authenticated and 
provides \ac{DEN-SS}.)
This would give confidentiality (or deniability) and integrity for the message, 
but if the first and the last node belong to Carol and David, they can infer 
that Alice sent a message to Bob.
Note that as our in-package header is designed, each node on the route can infer 
its position on the route \emph{relative to the destination}.
(We discuss how to remedy this below.)
None of the nodes can know if they are the first node or not, unless they 
collude with the previous node.
The last node, however, can know for sure that the next hop is the destination, 
but not who it belongs to.

@@

\subsection{Limitations}
from mails:  - Route fingerprinting in anonymous communications.

It depends on the random peer sampling I suppose. And I have no clue 
about how that one works. Adrien referred to a paper by Anne-Marie.

If I were to guess, I'd say: if Anne-Marie's RPS protocol is Byzantine 
fault tolerant, maybe; otherwise, we're most likely screwed.

> - Bridging and fingerprinting: Epistemic attacks on route selection

I'd say the same as above. It's about peer selection.

> - Breaking the collusion detection mechanism of morphmix

We don't do any collusion detection, so I'd say we're vulnerable. We 
assume we choose nodes uniformly at random, so colluding nodes have 
uniform probability of success --- but that falls back on the RPS and 
Anne-Marie's paper. So maybe or screwed.

> - Denial of service or denial of security? How attacks on reliability can
> compromise anonymity

After just reading the abstract, most likely vulnerable. But thanks to 
our stateless design we don't have to do retransmission the whole way, 
as might be the case for active circuits --- only the node who 
experience the failure going forward will need to retransmit. (Thanks 
Adrien for insisting on creating a route back for the ACK ;-)) So we 
might not be in as bad a position as other systems, it'll take more 
rounds of attack to break it --- but I'm quite sure it will break.

But in general, these all face global and possibly malicious 
adversaries. We don't have that in our adversary model. If everyone 
colludes against Alice and Bob in our setting, they're screwed.

It's basically impossible to remain anonymous against the global 
adversary (statistical inference, paper by Danezis) unless Alice sends a 
message to everyone whenever she wants to send a message to Bob. 
Basically the anonymous communication community is converging on methods 
like Loopix and HORNET --- have enough throughput so that the global 
adversary is overwhelmed with data. (Tor is too slow.)

\subsection{Future Work}
% \commentAL{To rewrite as real paragraphs} Future work and prospects:
% \begin{itemize}
% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
% 	\item Changing devices' asymmetric keys regularly would increase security.
% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver. To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.
